Which ITG Stepcharts are Turniest?

### 2017-03-14 itg/2/paper.tex
itg paper add a bunch of tables

Right, let's resume right where I left off in my last paper \cite{turniness}, shown in Figure~\ref{fig:you-stutid-fuckass}.
Unlike mainstream conferences, SIGBOVIK doesn't make me waste space repeating all the background material,
and I can just say go read that paper first and get back to me.
It's probably a lot funnier than this one anyway, which is gonna be sort of dry, and really of interest only to other ITG players.

\begin{figure}[h]
	\includegraphics[angle=90,width=0.48\textwidth]{../paper.pdf}
	\caption{(okay twist your head to read this)}
	\label{fig:you-stutid-fuckass}
\end{figure}

@@

@@

\texttt{~~~~~~~~~~f = nx * 2 > ns || nx * 2 == ns \&\& ((jacks s > switches s) /= lastFlip s)} \\

@@

>>>>

Right, let's resume right where I left off in my last paper \cite{turniness}, shown in Figure~\ref{fig:you-stutid-fuckass}.
Unlike mainstream conferences, SIGBOVIK doesn't make me waste space repeating all the background material,
and I can just say go read that paper first and get back to me.
It's probably a lot funnier than this one anyway, which is gonna be sort of dry,
and really of interest only to other ITG players who already know what's going on.

\begin{figure}[h]
	\hspace{-2em}\includegraphics[angle=90,width=0.54\textwidth]{../paper.pdf}
	\caption{(okay twist your head to read this)}
	\label{fig:you-stutid-fuckass}
\end{figure}

@@

Recall Table~\ref{tab:facing} from the last paper, in which I left undefined the facings for $LL$, $DD$, $UU$, and $RR$, the four footswitch footings.

@@

\texttt{~~~~~~~~~~f = nx * 2 > ns || nx * 2 == ns \&\& ((switches s > jacks s) == lastFlip s)} \\

@@

%\section{A Bit More on Turniness}

\section{Experimental Results}

% TODO: Put a * on charts where you're going to put a pict of mario man
% TODO: Put a dagger on footswitch charts where the footing is a clever reinterpretation, rather than intended
% TODO: Make a special mention of sandstorm and put a pict of mario man

\begin{figure}[t]
		\small
	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\
		\hline
		\multicolumn{5}{c}{\em no 8s- with $\ge$100 XOs} \\
		 9 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 107 & \em 8.7 \\
		10 & J-PARA SUPER MEGAMIX     & CuoReNeRo MeGaPacK    & \bf 141 & \em 3.9 \\
		11 & Somebody That I Used To Know & Best of Gazebo    & \bf 114 & \em 11.9 \\
		12 & Credens Justitiam        & Stuff B Likes         & \bf 136 & \em 12.4 \\
		13 & Banshee Strikes          & VocaJawnz             & \bf 152 & \em 10.2 \\
		14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		15 & MAX Forever              & CuoReNeRo MeGaPacK    & \bf 101 & \em 4.2 \\
		\multicolumn{5}{c}{\em no 16s-20s with $\ge$100 XOs} \\
		21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\
	\caption{Charts with the most total crossovers (XOs).}
\end{figure}
\begin{figure}[t]
		\small
	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XO & \bf XO\% \\
		\hline
		 4 & DAM DIRIRAM              & DDR 3rdMIX            & \em  30 & \bf 27.3 \\
		 5 & STRICTLY BUSINESS        & DDR 1st               & \em  33 & \bf 21.4 \\
		 6 & STRICTLY BUSINESS        & DDR 1st               & \em  38 & \bf 20.9 \\
		 7 & MOBO$\star$MOGA          & DDR EXTREME           & \em  37 & \bf 17.3 \\
		 8 & PARANOiA                 & DDR 1st               & \em  58 & \bf 19.6 \\
		 9 & Dazzlin Darlin           & r21twins              & \em  76 & \bf 22.0 \\
		10 & Enchanted Journey        & ITG Rebirth           & \em  78 & \bf 19.3 \\
		11 & Lune Noir                & r21freak Friendship   & \em  58 & \bf 13.4 \\
		12 & Winnipeg is Fucking Over & best of r21freak ii   & \em 122 & \bf 14.3 \\
		13 & The Sampling Paradise    & The Paradise Sampler  & \em 139 & \bf 15.6 \\
		14 & Slow Down                & Sexuality Violation 2 & \bf 160 & \bf 13.3 \\
		\multicolumn{5}{c}{\em no 15s-20s with $\ge$10\% XO} \\
		21 & Teenage Dream            & Sexuality Violation 2 & \bf 280 & \bf 11.8 \\
	\caption{Charts with the highest percentage of crossovers among total steps.}
\end{figure}
\begin{figure}[t]
		\small
	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\
		\hline
		\multicolumn{5}{c}{\em no 5s- with $\ge$50 FSs} \\
		 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		\multicolumn{5}{c}{\em no 7s-9s with $\ge$50 FSs} \\
		10 & Eat 'Em Up!      & Mute Sims 5           & \bf  54 & \em  9.0 \\
		11 & Nemeton          & The Legend of Zim 4   & \bf  97 & \em 10.3 \\
		12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		15 & Danse Macabre    & Aoreo's Ariginals     & \bf 201 & \em 12.2 \\
		16 & Weird Science    & Stamina Showcase      & \bf  61 & \em  1.8 \\
		\multicolumn{5}{c}{\em no 17s+ with $\ge$50 FSs} \\
	\caption{Charts with the most total footswitches (FSs).}
\end{figure}
\begin{figure}[t]
		\small
	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#FS & \bf FS\% \\
		\hline
		%\multicolumn{5}{c}{\em no <6s with >50 FSs} \\
		 3 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  26 & \bf 15.3 \\
		 4 & MAKE IT BETTER   & DDR 2ndMIX            & \em  26 & \bf 20.0 \\
		\multicolumn{5}{c}{\em no 5s with $\ge$10\% FS} \\
		 6 & Sweat Shop       & ITG Rebirth 2 Beta    & \bf  56 & \bf 18.2 \\
		 7 & 5.1.1            & DDR MAX               & \em  13 & \bf 12.9 \\
		\multicolumn{5}{c}{\em no 8s with $\ge$10\% FS} \\
		 9 & PARANOiA KCET    & DDR 2ndMIX            & \em  33 & \bf 10.2 \\
		10 & Delhi Ill        & Mute Sims 6           & \em  40 & \bf 11.6 \\
		11 & Sweat Shop       & ITG Rebirth 2 Beta    & \em  75 & \bf 11.8 \\
		12 & Nemeton          & Subluminal            & \bf 140 & \bf 14.8 \\
		13 & Love Is Eternity & Subluminal            & \bf 140 & \bf 16.8 \\
		14 & Switch           & Getty                 & \bf 347 & \bf 15.7 \\
		15 & Flames of the Sky & fort rapids vii      & \em 172 & \bf 16.5 \\
		\multicolumn{5}{c}{\em no 16s+ with $\ge$10\% FS} \\
	\caption{Charts with the highest percentage of footswitches among total steps.}
\end{figure}
\begin{figure}[t]
		\small
	\begin{tabular}{r|l|l|c|c}
		\bf Ft. & \bf Name & \bf Pack & \bf \#XF & \bf XF\% \\
		\hline
		\multicolumn{5}{c}{\em no 8s- with $\ge$12 XFs} \\
		 9 & Dr. Boom-Bombay   & fort rapids vii            & \bf 18 & 4.0 \\
		10 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.5 \\
		11 & Heart Shooter     & VocaJawnz                  & \bf 44 & 5.1 \\
		12 & Beautiful Synergy & Keyboard Collaboration III & \bf 14 & 3.2 \\
		13 & Toxic             & Sexuality Violation 2      & \bf 12 & 1.2 \\
		14 & Fancy Footwork    & Cirque du Zeppelin         & \bf 40 & 4.2 \\
		\multicolumn{5}{c}{\em no 14s+ with $\ge$12 XFs} \\
	\caption{Charts with the most crossover footswitches (XFs). (Here I chose 12 as the cut-off because below that are a bunch of false-positives from DDR.)}
\end{figure}
